Verifying Demonstrations

### 2018-11-28 paper/adversary-model.tex
harmonizing submittable

We now provide a concretely defined system and adversary model.
We give three definitions, each defines an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{base-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{base-adversary}
  \emph{Base adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data (such as who sent it).

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  %(\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still learns only the protocol data, no auxiliary data.

\item\label{deanonymizing-adversary}
  \emph{Fully deanonymizing adversary}:
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}

@@

We find \cref{base-adversary} suitable when the protester and witness both move 
in a crowd and there is no way for the witness to decide exactly with whom he 
or she communicates with.
However, in some situations this might not be the case: \Eg if the crowd is not 
dense the witness will likely see the face of the protester.
If the witness is controlled by the adversary, then it is likely that the 
witness can capture a picture of the face, which can be turned into an identity 
through face recognition.
There are various such scenarios leading to the adversary learning the 
protester's identity, we capture this as 
\cref{deanonymizing-witness-adversary}.

As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
control the channel between \(P\) and \(S\), \eg when \(P\) uses 
Tor~\cite{Tor}.
The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
jurisdiction.

However, given a strong enough adversary, such anonymous communication might 
not be possible; \eg if the adversary can do a time-correlation attack.
We capture such a strong adversary as \cref{deanonymizing-adversary}.

>>>>

We now provide a concretely defined system and adversary model.
We give three definitions, each defining an adversary with increasingly stronger 
capabilities (\ie more auxiliary information).

There are three players: the protest participant (with identity) \(P\), a 
witness (with identity) \(W\) and the storage \(S\).
The adversary \(A\) controls \(W\) and \(S\).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the base adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time it happened, \(t_{P,S}\).
    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
    \(A\).
  }
\end{figure}

\begin{definition}[Base adversary]%
  \label{base-adversary}
  The protester \(P\) and the witness \(W\) communicate.
  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
  communication occurred \(t_{P,W}\)\footnote{%
    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
    directly from the communication medium, only if those appear in the data 
    \(d_{P,W}(\cid, P)\).
  }.
  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
  communication (\(t_{P,S}\)) but not the real identities.
  The adversary controls \(W\) and \(S\) and thus learns everything that they 
  do, but can additionally correlate what he learns from \(W\) and \(S\).
\end{definition}

@@

We find \cref{base-adversary} suitable when the protester and witness both move 
in a crowd and there is no way for the witness to decide exactly with whom he 
or she communicates with.
However, in some situations this might not be the case: \Eg if the crowd is not 
dense the witness will likely see the face of the protester.
If the witness is controlled by the adversary, then it is likely that the 
witness can capture a picture of the face, which can be turned into an identity 
through face recognition.
There are various such scenarios leading to the adversary learning the 
protester's identity, we capture this by the following definition.

\begin{definition}[Deanonymizing-witness adversary]%
  \label{deanonymizing-witness-adversary}
  The situation is the same as in \cref{base-adversary}, but now the witness 
  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
  (\(P\) will also learn \(W\)'s identity.)
  However, \(S\) still does not learn \(P\)'s identity.
\end{definition}

\daniel{The deanonymizing witness captures: a1, a4, a5. (See Simon's notes on 
  Slack.)}

One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous communication.
However, given a strong enough adversary, such anonymous communication might not be possible.
We capture such a strong adversary in the following definition.

\begin{definition}[Deanonymizing adversary]%
  \label{deanonymizing-adversary}
  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
\end{definition}

\daniel{The deanonymizing adversary additionally captures: a2, a3 (\ie a1, a2, 
  a3, a4, a5).}

### 2018-11-28 paper/intro.tex
harmonizing submittable

The paper is organized as follows.
First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting. Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS. 
We then formalize the notion of protest and the desired verifiability and privacy properties in \cref{definitions}, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
% Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
% We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
% \daniel{Check that this is true before publication.} 
% and formally verify it using Tamarin~\cite{TamarinDB}.
% \seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}) and performance (\cref{PerformanceAnalysis}) .
Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

>>>>

The paper is organized as follows.
First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}). Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}). 
We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}). 
% Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
% We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
% \daniel{Check that this is true before publication.} 
% and formally verify it using Tamarin~\cite{TamarinDB}.
% \seb{we need to be careful about the above sentence}
%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
After that, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks (\cref{Protocol}), before analyzing its security and privacy (\cref{SecurityAnalysis}), and its performance (\cref{PerformanceAnalysis}).
Finally, we discuss our assumptions and results (\cref{Discussion}) and give our conclusions (\cref{Conclusion}).
%\sonja{add (sub) sections for performance and verification}

### 2018-11-28 paper/protest-model.tex
harmonizing submittable

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,\label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.

@@

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).
  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
\end{definition}

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
(Note that a participant of a protest can take the role of a protester but also 
act as witness for other protesters.)
All the proof shares together form the participation proof.

@@

\begin{definition}[Proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).
  We define \(\pshs\) as the set of all proof shares.
\end{definition}

A subset of the proof shares forms a participation proof for a protester.
We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \\
  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, time interval \(t\) and location \(l\) within those of the protest (\ie any subprotest).
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define the \emph{participation count} of a protest \(\prtst\) (as in \cref{DefParticipationProof}) as the cardinality 
  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
      \str(\prf_{i,P})\geq \theta \right\}
  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
  threshold \(\theta\).
\end{definition}

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

\simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}
\daniel{Fixed formula, math mode; didn't check Section V though.}

>>>>

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause,\label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.

@@

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} \(p = (\cid, t, l)\) is a tuple in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).\\
  A \emph{protest} \(\prtst\) is the set of subprotests sharing the same \(\cid\).
\end{definition}

@@

Our protocol relies on \emph{witnesses} to certify and associate the proof to the time and location by creating a \emph{proof share}.
A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
(Note that a participant of a protest can take the role of a protester but also 
act as witness for other protesters.)
Then, the set of all \emph{eligible} proof shares forms the participation proof of a protester.

@@

\begin{definition}[Eligible proof share]%
  \label{DefProofShare}\label{DefProofShares}
  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
  \(\cid, t, l\) are as in \cref{DefProtest};
  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
  Furthermore, we say that \(\psh\) is \emph{eligible} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
  \(\psh \sqsubseteq \sprtst\).

\end{definition}

%A subset of the proof shares forms a participation proof for a protester.
We denote by \(\pshs\) the set of all proof shares,
and we will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
\begin{multline*}
  \pshs_{\cid_0, \pid_0} = \\
  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
\end{multline*}

% proof
% proofs
\begin{definition}[Participation proof]%
  \label{DefParticipationProof}\label{DefParticipationProofs}
  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
  set
  \begin{equation}
    \nonumber
    \prf_{\pid, \prtst} =
    \left\{ \psh \in \pshs_{\cid, \pid} \mid
      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
  \end{equation}
  of all proof shares with the same protester and protest identifiers, and eligible for any subprotest $p$ of $\prtst$.
  We denote by \(\prfs\) the set of all proofs.
\end{definition}

@@

We can now define the participation count as follows.
\begin{definition}[Participation count]%
  \label{DefParticipationCount}
  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{valid} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
      \str(\prf_{i,\prtst})\geq \theta \right\}
  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
\end{definition}

The strength function \(\str\) can be used to regulate the trust in the 
participation count estimated. In general, \(\str\) can be defined as a 
weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
weights \(\omega_i\) being the trust in the witness corresponding to that proof 
share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
to accept a participant as valid.
One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
Finally, both approaches can be combined by giving a weight of 1 to all 
non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
results in a participant being valid if they are witnessed either by \(\theta\) 
non-trusted witness or by one trusted witness.

\simon{check that the description in section V corresponds}

### 2018-11-28 paper/system-model.tex
harmonizing submittable

\section{System and adversary model}%
\label{system-model}

To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.

@@

\subsection{Desired properties}

We note that, in general terms, protesting is very similar to petitions, which 
in turn are similar to voting.
Indeed, all three situations correspond to situations in which many individuals express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.

We draw inspiration from the three traditionally desired properties for verifiability for voting:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
The eligibility requirement is slightly different as for protests it must 
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

@@

Coercion resistance is not possible to achieve for protests.
For instance, someone could simply physically bring Alice to a protest against her will.
Receipt freeness, while appealing at first glance, is not desirable (probably 
not possible) in our context since this will conflict with verifiability: in 
contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which conflicts with verifiability.

Thus, in our context the crucial property is therefore privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the participation 
proof (and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (\eg 
from a different protest).

\subsection{Adversary model}%
\label{adversary-model}

We consider two types of adversaries: 
\begin{enumerate*} 
\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
\end{enumerate*}

>>>>

\section{System model and requirements}%
\label{system-model}

To set the stage, we will now describe our system model including
assumptions and a summary of the desired properties for crowd
counting% and the adversary model
.

@@

\subsection{Desired properties}%
\label{desired-properties}

We note that, in general terms, protesting is very similar to signing petitions, which 
in turn is similar to voting.
Indeed, all three practices correspond to situations in which many individuals express their opinion, which can be sensitive (\eg be a cause for discrimination or persecution), and thus need to be protected.
Hence the desire for similar properties of verification and privacy for a protest as for voting.

We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
\daniel{Find a new ref for voting verifiability properties, Douglas commented 
  that the last one is not the origin.}
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
      old.}
  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
      Fiat-Shamir (technically). Non-technically, much older.}
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal\footnote{%
  Elections also have some temporal aspects, such that one cannot vote at any 
  time and a vote in one election should not be reusable in the next election.
  However, the temporal relation for a protest is not as strictly defined as for 
  elections as a protest can start at any time and last for an arbitrary period 
  of time.%
} and spatial eligibility (\ie each participation proof satisfies some temporal 
and spatial relation to the protest).
In essence, the proof must bind the person to the time and location of the protest.

@@

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting boots), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

Therefore in our context, the crucial property is  vote privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity \(P\) and the participation 
proof (and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (from a different protest).

% \subsection{Adversary model}%
% \label{adversary-model}

% We consider two types of adversaries: 
% \begin{enumerate*} 
% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
% \end{enumerate*}
